Cartograms with Dynamic Features

### 2022-05-18 paper/section/main.tex
draft: add river translation in algo

\bobgraph{Initialization:} We first load and render the CCG geospatial boundaries. For each CCG we compute the centroid and represent it using a square node, $ \node $, with the initial size, $ \nodeSize $. \new{We then load the river shapefiles and render the rivers. Since the vertices of the river in the shapefiles are not in sequential order, we first render the starting vertex, followed by the next closest vertex. This rendering approach enables us to adjust the river resolution as shown in \figref{fig:river resolution}. We further apply a smoothing logic by removing vertices that are too close to each other.}

@@

@@

{
\begin{figure}[tb!]
    \centering
    \includegraphics[width=\columnwidth]{figure/river_resolution.png}
    \caption{The resolution of rivers can be dynamically adjusted by the user. A shows River Thames at its original resolution with 10,170 edges. B shows the river at a reduced resolution of 49 edges. \new{We further smooth the river by removing vertices in dense areas, as shown in C.} The reduced resolution preserves the majority of River Thames' original shape and improves the performance of our river intersection tests.}
    \label{fig:river resolution}
\end{figure}
}

% \begin{noindent}
\begin{algorithm}[tb!]
    \caption{Procedure to test if a node's translation path, $ \nodeLineNV $ intersects a river.}\label{alg:check river intersection}
    \textbf{Input:} \\
    $ \nodeLineNV \gets $ the node's translation path \\

@@

    \textbf{Global variables:} \\
    $ \riverEdgeList \gets $ a list of river edges \\

    \textbf{Local variables:} \\
    $ \riverEdgeLine \gets $ a river edge in $ \riverEdgeList $ \\ 
    $ \nodeBoundingBox, \riverEdgeBoundingBox \gets $ the bounding boxes for $ \nodeLineNV $ and $ \riverEdgeLine $ \\
    % $ \boundingBoxInt \gets $ boolean indicating $ \nodeBoundingBox $ intersects $ \riverEdgeBoundingBox $ \\
    % $ \nodeEdge \gets $ the edge for $ \node $\\
    % $ \edgeBoxInt \gets $ boolean indicating $ \nodeEdge $ intersects $ \riverEdgeListEach $ \\

    \begin{algorithmic}[1]
        \Procedure{TestIntersection}{$ \nodeLineNV $}

        \ForEach{$ \riverEdgeLine \in \riverEdgeList $}
            \State $ \nodeBoundingBox \gets $ GetBoundingBox ($ \nodeLineNV $)
            \State $ \riverEdgeBoundingBox \gets $ GetBoundingBox ($ \riverEdgeLine $)

            \If{$ \nodeBoundingBox ~intersect~ \riverEdgeBoundingBox = True $}
                \State \Return{$ \nodeLineNV ~intersect~ \riverEdgeLine $}
                \EndIf
        \EndFor

>>>>

\bobgraph{Initialization:} We first load and render the CCG geospatial boundaries. For each CCG we compute the centroid and represent it using a square node, $ \node $, with the initial size, $ \nodeSize $. We then load the river shapefiles and render the rivers. Since the vertices of the river in the shapefiles are not in sequential order, we first render the starting vertex, followed by the next closest vertex. This rendering approach enables us to adjust the river resolution as shown in \figref{fig:river resolution}. We further apply a smoothing logic by removing vertices that are too close to each other.

@@

    \begin{algorithm}[tb!]
        \caption{Procedure to adjust river positions, remove node overlap and prevent nodes from crossing rivers.}\label{alg:UpdateLayout}
        \textbf{Global variables:} \\
        $ \nodeList \gets $ a list of $ \node $ representing CCGs with the following properties: \\
        \-\hspace{1em}  \textcolor{blue}{$\nodeListCross \gets $ the number of $ \node $ in $ \nodeList $ that crosses a river} \\
        $ \nodeSize \gets $ the current size of all nodes \\
        $ \nodeSizeMax \gets $ the maximum size of a node \\
        \textcolor{blue}{ $ \riverList \gets $ a list of $ \river $ representing river features} \\
        $ \stalemateMax \gets $ the maximum number of iterations indicating a stalemate \\

        \begin{algorithmic}[1]
            \Procedure{UpdateLayout}{}
            \While{$ \nodeSize < \nodeSizeMax $}
                \State \textcolor{blue}{$ \nodeListCross \gets 1 $ \Comment{Trigger the while loop}}
                \While{$ \nodeListCross > 0 $}

                    \State $ \nodeListCross \gets 0 $
                    \State $ \nodeList \gets $ RemoveOverlap ($ \nodeList $)
                    \color{blue}
                    \ForEach {$ \river \in \riverList $}
                        \State $ \riverVector \gets (0,0) $ \Comment{Hold the sum of vectors $ \nodeVectorCT $}
                        \ForEach {$ \node \in \nodeList $}

                            \If {$ \node(x,y) \neq \nodeFNOR(x,y) $}
                                \If{ \Call{TestIntersection}{$ \nodeFNORLine $, $ \river $} $ = True $}
                                \State $ \riverVector \gets \riverVector + \nodeVectorCT$
                                \State $ \nodeListCross \gets \nodeListCross ++ $
                                \EndIf

                        \State Translate river $ \river $ by the average vector $ \frac{\riverVector}{\nodeListCross} $
                        \State $ \nodeListCross \gets 0 $ \Comment{Clear the counter}
                    \EndFor

                    \color{black}
                    \ForEach {$ \node \in \nodeList $}

                            \If{ \Call{TestIntersection}{$ \nodeFNORLine $} $ = True $}
                                \State $ \nodeCross \gets \nodeCross ++ $
                                \State $ \nodeListCross \gets \nodeListCross++ $

@@

{
\begin{figure}[tb!]
    \centering
    \includegraphics[width=\columnwidth]{figure/river_resolution.png}
    \caption{The resolution of rivers can be dynamically adjusted by the user. A shows River Thames at its original resolution with 10,170 edges. B shows the river at a reduced resolution of 49 edges. We further smooth the river by removing vertices in dense areas, as shown in C. The reduced resolution preserves the majority of River Thames' original shape and improves the performance of our river intersection tests.}
    \label{fig:river resolution}
\end{figure}
}

% \begin{noindent}
\begin{algorithm}[tb!]
    \caption{Procedure to test if a node's translation path, $ \nodeLineNV $ intersects a river.}\label{alg:check river intersection}
    \textbf{Input:} \\
    $ \nodeLineNV \gets $ the node's translation path \\
    $ \river \gets $ a river feature \\

@@

    \textbf{Local variables:} \\
    $ \nodeBoundingBox, \riverEdgeBoundingBox \gets $ the bounding boxes for $ \nodeLineNV $ and $ \Edge $ \\
    $ \Edge \gets $ an edge of $ \river $ \\

    \begin{algorithmic}[1]
        \Procedure{TestIntersection}{$ \nodeLineNV $, $ \river $}

        \ForEach{$ \Edge \in \river $}
            \State $ \nodeBoundingBox \gets $ GetBoundingBox ($ \nodeLineNV $)
            \State $ \riverEdgeBoundingBox \gets $ GetBoundingBox ($ \Edge $)

            \If{$ \nodeBoundingBox ~intersect~ \riverEdgeBoundingBox = True $}
                \State \Return{$ \nodeLineNV ~intersect~ \Edge $}
                \EndIf
        \EndFor
